---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# rdimensions

R client for interacting with the [Dimensions](https://www.dimensions.ai/) Analytics API.

Inspired by the [Dimcli python client](https://github.com/digital-science/dimcli)

** Work in progress **

## Prerequisites

Access to the Dimensions Analytics API requires that you have a Dimensions account with the necessary authorization privileges.

At the current time, Dimensions offers free access to the Analytics API for scientometric researchers and research projects. To apply for free access, visit [this page](https://www.dimensions.ai/scientometric-research/) and click on 'request access'. You will be required to fill in an application to request no-cost use of Dimensions.

Note that Dimensions has an agreement with the [International Society for Scientometrics and Informetrics](http://issi-society.org/) (ISSI) to provide no-cost access to all ISSI members directly. 

## Installation

Install the development version from Github:

```{r eval=FALSE}

install.packages("devtools")
devtools::install_github("nicholasmfraser/rdimensions")

# current install with private credentials - use token c68300163e025ce67bd912e357e269e3e8054e4e 


```

## Authentication

Prior to making any queries, you must login with your Dimensions credentials. You can login using the `dimensions_login()` function, which takes a list of credentials (username and password) as arguments:

```{r eval=FALSE}

dimensions_login(credentials = list(
  "username" = "your_username",
  "password" = "your_password"
))

```

Alternatively, you can store your username and password in your .Renviron file, as follows:

```{r eval=FALSE}

dimensions_username=your_username
dimensions_password=your_password

```

You can then login simply with the command `dimensions_login()`, without manually supplying your credentials.

## Queries

For interacting with the Dimensions Analytics API, `rdimensions` currently provides two main functions: `dimensions_query()` and `dimensions_iterate()`. The difference between these functions is that `dimensions_query()` will make a single query request and retrieve the first page of results. Dimensions limits the number of records returned for a single query to 1000. For queries where you wish to retrieve a larger number of records, you can instead use `dimensions_iterate()` to iterate through multiple results pages, and return all results in a single object.

This function takes two arguments: `query` and `format`:

* `query` is a string containing a complete Dimensions Search Language (DSL) query. Full information on the DSL structure can be found [here](https://docs.dimensions.ai/dsl/). In general, DSL queries consist of two parts, a `search` phrase, and a `return` phrase. The `search` phrase specificies the documents that we would like to know about. The `return` phrase specifies what we want to know about those documents. A simple example of a DSL query would be `search publications for "bibliometrics" return publications [doi + title + year]`. In this query, we would search all publications for those related to bibliometrics, and for any publications found, return the doi, title and year of publication.

* `format` specifies the format in which data should be returned, currently limited to `list` or `json` types. The default format is `list`.

Some examples of potential queries are shown below. Note that when using `dimensions_raw`, any quotation marks that are necessary parts of a DSL query must be escaped by placing a backwards slash before each quotation mark, e.g. `"bibliometrics"` becomes `\"bibliometrics\"`. 

```{r eval=FALSE}

# A basic query
dimensions_raw("search publications return publications")

# Return data in JSON format
dimensions_raw("search publications return publications", format = "json")

# By default Dimensions limits results to a maximum of 20 records
# You can increase this using the 'limit' argument, up to a maximum of 1000 records
dimensions_raw("search publications return publications limit 500")

# Search for other source types
dimensions_raw("search grants return grants")
dimensions_raw("search patents return patents")
dimensions_raw("search policy_documents return policy_documents")
dimensions_raw("search clinical_trials return clinical_trials")
dimensions_raw("search researchers return researchers")

# Apply filters
dimensions_raw("search publications where year in [2010:2015] return publications")

# Search for a specific DOI
dimensions_raw("search publications where doi = \"10.3389/frma.2018.00023\" return publications")

# Search for a keyword
dimensions_raw("search publications for \"bibliometrics\" return publications")

```

## Roadmap

## Collaboration

Collaborators are extremely welcome! Please contribute here directly, or contact me at nicholasmfraser@gmail.com for more information.
